The Power of Unbiased Recursive Partitioning:\\ A Unifying View of CTree, MOB, and GUIDE

### 2019-05-11 pkg/partykit/inst/guideliketest/draft/draft.Rnw
revised Section 4.2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2551 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 82b94f655d8fb580fb2a901ac49e6b99045444e7

\subsection{Evaluation}
\label{sec:evaluation}
The testing strategies are evaluated over a stepwise increasing effect size $\delta$, 
on 100 data sets per step each consisting of 250 observations. 
To compare the performance of the evaluated testing strategies for each step 
the $p$-values corresponding to the true split variable $Z_1$ and the proportion
of data sets for which $Z_1$ is detected and also selected 
%(for a given significance level $\alpha = 0.05$) 
is considered for the first scenario (stump).
For the second scenario (tree with 2 splits) the Adjusted Rand Index~(ARI) is calculated 
as a measure of similarity between the true tree structure and the fitted model tree.

>>>>

\subsection{Evaluation}
\label{sec:evaluation}
The testing strategies are evaluated over a stepwise increasing effect size $\delta$, 
on 100 replications per step each consisting of 250 observations. 
To compare the performance of the evaluated testing strategies for each step 
in the first scenario (stump with 1 split) the following criteria are considered:
the $p$-values pertaining only to the true split variable $Z_1$;
and the proportion of data sets for which the $p$-value of $Z_1$
is the lowest and significant at 5\% level (i.e., where $Z_1$ would be
selected for splitting in a pre-pruning approach).
For the second scenario (tree with 2 splits) the adjusted Rand index~(ARI) is calculated 
as a measure of similarity between the true tree structure and the fitted model tree.
